\mytitle{}

### 2018-11-14 paper/paper.tex
And, done.
Some notes...

\subsection{Per-feature pre-training}
To investigate the effects of pre-training individual features, we chose our four best-performing features (global state, mean IAT, $\Delta$ in/out rates) and trained each over \num{10000} iterations, before evaluating the policy obtained by summing the action values suggested by each.
This may be achieved in a real network by randomly assigning new hosts to be controlled exclusively by one feature's policy, allowing agents to more easily learn \emph{which} information led to the correct action being taken.
To reflect this (and train all parts of an agent in the same time frame), we reduce the timestep length to \SI{10}{\milli\second} to train each agent in less wall-clock time, at the cost of noisier data (and reduced learning rate).
The results show no real change for Marl++, but a considerable gain for SPF (though smaller than a single learner).
%It's most likely that SPF is sensitive to noisy data when trying to learn how to act on TCP, and that as the different protocols did in \cref{fig:udp-feature-plots,fig:tcp-cap-feature-plots}, Marl++ and SPF have different optimal feature sets for different traffic behaviours---many of which may have been excluded.

@@

	\caption{
		Mean Marl action values from pre-training on mean IATs ($n=16$).
		As these are mean values, lighter cells in each row indicate actions \emph{likely} to be taken by an agent's policy.
		Repeated values originate from the bias tile, which is always active, and indicate regions of the state-space which have yet to be visited---here, this is most of the state space.
		The measured effectiveness of this feature then suggests that a low-resolution coding over the standard region may, in fact, be a better choice.
		We see that agents prefer to choose $p=0.0$ in most states, but higher $p$ when IATs are particularly small.
		\label{fig:intern-16-tcp-iat}
	}
\end{figure}

@@

	\caption{
		Mean Marl action values from pre-training on $\Delta$ out rates ($n=4$).
		A sudden ramp-up of server-to-host traffic is used as a strong indicator of flow legitimacy, while more punishing actions have comparatively higher value as $n$ decreases.
		Furthermore, we see again that a region of the state space has gone somewhat unexplored---we observed after plotting this visualisation that many decreases in this feature are too small to hit the adjacent tile, which implies a mixed-resolution coding may improve an agent's policy further.
		\label{fig:intern-16-tcp-something}
	}
\end{figure}

>>>>

\subsection{Per-feature pre-training}
To investigate the effects of pre-training individual features, we chose our four best-performing features (global state, mean IAT, $\Delta$ in/out rates) and trained each over \num{10000} iterations, before evaluating the policy obtained by summing the action values suggested by each.
This may be achieved in a real network by randomly assigning new hosts to be controlled exclusively by one feature's policy, allowing agents to more easily learn \emph{which} information led to the correct action being taken.
To reflect this (and train all parts of an agent in the same time frame), we reduce the timestep length to \SI{10}{\milli\second} to train each agent in less wall-clock time, at the cost of noisier data (and reduced learning rate).
The results show little change for Marl++, but generally indicate a considerable gain for SPF (though smaller than what we'd measured for a single agent system).
%It's most likely that SPF is sensitive to noisy data when trying to learn how to act on TCP, and that as the different protocols did in \cref{fig:udp-feature-plots,fig:tcp-cap-feature-plots}, Marl++ and SPF have different optimal feature sets for different traffic behaviours---many of which may have been excluded.

@@

	\caption{
		Mean Marl action values from pre-training on mean IATs ($n=16$).
		As these are mean values, lighter cells in each row indicate actions \emph{likely} to be taken by an agent's policy.
		Repeated values originate from the bias tile, which is always active, and indicate regions of the state-space which have yet to be visited---here, this is most of the state space.
		Agents visibly learn action values for tiles which override the default bias tile's preferences.
		The measured effectiveness of this feature then suggests that a low-resolution coding over the standard region may, in fact, be a better choice.
		We see that agents prefer to choose $p=0.0$ in most states, but higher $p$ when IATs are particularly small.
		\label{fig:intern-16-tcp-iat}
	}
\end{figure}

@@

	\caption{
		Mean Marl action values from pre-training on $\Delta$ out rates ($n=4$).
		A sudden ramp-up of server-to-host traffic is used as a strong indicator of flow legitimacy, while more punishing actions have comparatively higher value as $\Delta$ out rate decreases.
		Furthermore, we see again that a region of the state space has gone somewhat unexplored---we observed after plotting this visualisation that many decreases in this feature are too small to hit the adjacent tile, which implies a mixed-resolution coding may improve an agent's policy further.
		\label{fig:intern-16-tcp-something}
	}
\end{figure}
